%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                             Curriculum Vitae                               %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[10pt,a4]{article}
\topmargin-2.0cm
\advance\oddsidemargin-1.2cm
\advance\evensidemargin-1.2cm
\textheight9.22in
\textwidth6.4in
\newcommand\bb[1]{\mbox{\em #1}}
%\def\baselinestretch{1.25}
\def\baselinestretch{1.0}

\usepackage{multicol}
% The use of the times package forces the use of the type-1 times
% roman font, but the times roman font does not look nice.
% Besides the times roman font still does not print correctly on
% the dopy printer.
%\usepackage{times}

\usepackage{fancyhdr}
\usepackage[dvips]{color}

\newcounter{myEnumCounter}
\newcounter{mySaveCounter}
\renewenvironment{enumerate}{%
  \begin{list}{\arabic{myEnumCounter}.}{\usecounter{myEnumCounter}%
  \setcounter{myEnumCounter}{\value{mySaveCounter}}}
  }{%
  \setcounter{mySaveCounter}{\value{myEnumCounter}}\end{list}%
}
\newcommand\myEnumReset{\setcounter{mySaveCounter}{0}}

% The old enumerate environment is rewritten, so you need no special command to
% start continuing counting. With the command \myEnumReset you can Reset the couter
% at any place in the text.

% http://www.educat.hu-berlin.de/~voss/lyx/list/enum.phtml

\definecolor{gray}{rgb}{0.4,0.4,0.4}

\begin{document}

%\thispagestyle{empty}
%\pagestyle{plain}

\thispagestyle{fancy}
%\pagenumbering{gobble}
%\fancyhead[location]{text}
% Leave Left and Right Header empty.
%\lhead{\textcolor{gray}{\it Sundar Iyer}}
%\rhead{\textcolor{gray}{\thepage/\totalpages{}}}
%\rhead{\thepage}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize \textcolor{gray}{}}
%A copy of this curriculum vitae, publications and 
%talk slides are available for download at
%http://www.stanford.edu/$\sim$sundaes/application}}


%\pagestyle{myheadings}
%\markboth{Sundar Iyer}{Sundar Iyer}

\vspace*{0.4cm}
\begin{center}
{\huge \bf Kangkook Jee}
\vspace*{0.25cm}
\end{center}

\begin{small}

%===================================
\begin{tabbing}
\=xxxxxxxx\=xxxxxxxx\=xxxxxxxx\=\kill
\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}

1214 Amsterdam Ave. Mailcode: 0401  & Phone: (212) 939-7054 \\
New York, NY-10027 &  Email: jikk@cs.columbia.edu\\
http://www.cs.columbia.edu/$\sim$jikk & Alt: kangkook.jee@gmail.com \\
\end{tabular*}
\end{tabbing}

\vspace*{0.2cm}

%==========================================

\subsection*{PARTICULARS}

\hrule
\vspace{0.2cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsubsection*{EDUCATION}

\begin{tabbing}
xxxx\=xxxxxxxx\=xxxxxxxx\=xxxxxxxx\=\kill

\>\begin{tabular*}{0.9\linewidth}{l@{\extracolsep{\fill}}r}
Columbia University & New York, NY \\
Ph. D. in Computer Science  &  {\it 2008-, Defending May 2014}\\
 & \\

Columbia University & New York, NY \\
M. S. in Computer Science & {\it May 2008}\\
 & \\

Korea University, & Seoul, South Korea \\
B. Sc. majoring Mathematics minoring Computer Science & {\it  Mar 2001}
\end{tabular*}
\end{tabbing}

\subsubsection*{CURRENT STATUS}
\begin{list}{}{}
\item Citizen of South Korea.
\end{list}

\subsubsection*{RESEARCH INTERESTS}
%\hrule
%\vspace{0.2cm}

\begin{list}{}{}
% Do I have to specifically mention DFT or Symbolic execution?
\item My research interest lies in protecting software systems from either
  malcious attempts of attacker outside or unintended accidents due to
  programmer mistakes. To implement systems that enhance defense capabilities of
  softwares, I leverages tools from different software substrates which include
  VM hypervisors, OS kernel, software compilers.
\end{list}

\subsection*{WORK EXPERIENCE}
\hrule
\vspace{0.2cm}
\begin{itemize}
\item {\bf Second line support engineer, IBM Korea},
  Mar. 2001 - July. 2003. \\
 Worked for local support team that resolved serious issues from AIX operating
 systems, IBM Java Virtual Machine(JVM), and IBM high availability solutions.
\item {\bf Software Engineer, IBM Korea}, Mar. 2001 - July. 2003. \\

\end{itemize}

%\vspace{0.1cm}
\subsection*{RESEARCH EXPERIENCE}
\hrule
\vspace{0.2cm}
\begin{itemize}
\item {\bf Master Student Research Assistant, Columbia University}, Sep 2007 - May 2008. \\
%
  {\bf Application Community}, (Sep 1998 - June 2000): We ask the question as to
  whether it is possible to build a large switch from multiple smaller switches
  stacked in parallel, called the parallel packet switch (PPS), such that it
  behaves exactly like a large switch. I designed an algorithm and derived the
  first analytical proof of the conditions under which this is possible. I then
  extended this work so that the PPS can support quality of service and
  multicast traffic. Later, I derived and analyzed a practical distributed
  algorithm for the PPS. This research demonstrates how switching capacity can
  be scaled in an efficient manner.

\vspace{0.1cm}
\item  {\bf Research Assistant, Columbia University}, June 2007 - Current. \\
%
  {\bf Taint Flow Algebra}, (Jan 2001 - Mar 2002): From a network designer's
  perspective a shared memory router is ideal in that the packets are stored in
  a central location and the memory bandwidth and space is shared across packets
  from all ports. This sharing helps in conserving memory space and results in
  low cost and low power routers. However, it is a widely held myth that such
  shared memory routers are not scalable to higher speeds due to limitations
  imposed on the speed of a single memory. I worked on the first demonstration
  and proof to show how to build and scale the capacity of shared memory routers
  using distributed memories. \\
%
  {\bf ShadowReplica}, (Jan 2001 - Mar 2002): From a network designer's
  perspective a shared memory router is ideal in that the packets are stored in
  a central location and the memory bandwidth and space is shared across packets
  from all ports. This sharing helps in conserving memory space and results in
  low cost and low power routers. However, it is a widely held myth that such
  shared memory routers are not scalable to higher speeds due to limitations
  imposed on the speed of a single memory. I worked on the first demonstration
  and proof to show how to build and scale the capacity of shared memory routers
  using distributed memories. \\
%
  {\bf Comparison Study for Different Dynamic Binary Instrumentation(DBI)
    Systems}, (Jan 2001 - Mar 2002): From a network designer's perspective a
  shared memory router is ideal in that the packets are stored in a central
  location and the memory bandwidth and space is shared across packets from all
  ports. This sharing helps in conserving memory space and results in low cost
  and low power routers. However, it is a widely held myth that such shared
  memory routers are not scalable to higher speeds due to limitations imposed on
  the speed of a single memory. I worked on the first demonstration and proof to
  show how to build and scale the capacity of shared memory routers using
  distributed memories.\\
%
  {\bf A tool for runtime detection of integer errors written in C/C++}, (Jan
  2001 - Mar 2002): From a network designer's perspective a shared memory router
  is ideal in that the packets are stored in a central location and the memory
  bandwidth and space is shared across packets from all ports. This sharing
  helps in conserving memory space and results in low cost and low power
  routers. However, it is a widely held myth that such shared memory routers are
  not scalable to higher speeds due to limitations imposed on the speed of a
  single memory. I worked on the first demonstration and proof to show how to
  build and scale the capacity of shared memory routers using distributed
  memories.

\end{itemize}


%\vspace{0.1cm}
\subsection*{TEACHING EXPERIENCE}
\hrule
\vspace{0.2cm}

\begin{itemize}

\item {\bf Instructor.} COMS 3103-3: Programming Languages: Python , Fall 2013,
  Columbia University.

\item {\bf Teaching Assistant.} COMS 4701: Artificial Intelligence, Prof. Sal Stolfo
Spring 2013, Columbia University.

\item {\bf Teaching Assitant} COMS 3157-1: Advanced Programming, Prof Angelos
  D. Keromytis

\end{itemize}


% List of papers and publications and patents ?
%===========================================
%\vspace{0.1cm}
\subsection*{PUBLICATIONS}
\hrule
\vspace{0.2cm}

\subsubsection*{PAPERS}

\begin{enumerate}
    \item 
Sundar Iyer, Nick McKeown,
``Analysis of the Parallel Packet Switch Architecture",
to appear in {\it IEEE/ACM Transactions on Networking}, Apr. 2003.

    \item 
Sundar Iyer, Nick McKeown,
``Using Constraint Sets to Achieve Delay Bounds in CIOQ Switches", 
to appear in {\it IEEE Communication Letters}, 2003.

    \item 
Sundar Iyer, Supratik Bhattacharrya, Nina Taft, Christophe Diot,
``An Approach to Alleviate Link Overload as Observed on an IP Backbone". To appear in
{\it proceedings of IEEE INFOCOM}, San Francisco, March 2003. A more detailed
version of this paper appears in two technical reports as, ``An Approach to
Alleviate Link Overload as Observed on an IP Backbone ", {\it Sprint ATL
TR02-ATL-071127}, July 2002 and ``A Measurement Based Study of Load Balancing on an IP Backbone", {\it Sprint ATL TR02-ATL-051027}, May 2002.


    \item 
Sundar Iyer, Rui Zhang, Nick McKeown,
``Routers with a Single Stage of Buffering", 
{\it Proceedings of ACM SIGCOMM}, Pittsburgh, Pennsylvania, Sep 2002. Also in
{\it Computer Communication Review}, vol. 32, no. 4, Oct 2002.


    \item 
Sundar Iyer, Nick McKeown,
``On the Speedup Required for a Multicast Parallel Packet Switch", 
{\it IEEE Communication Letters}, June 2001, vol. 5, no. 6, pp. 269-271.

    \item 
Sundar Iyer, Ramana  Rao, Nick McKeown,
``Analysis of a Memory Architecture for Fast Packet Buffers", 
{\it IEEE - High Performance Switching and Routing}, Dallas, May 2001, pp.
368-373. A more detailed version of this work was presented in the {\it IEEE GBN
Workshop}, Alaska, April 2001.

    \item 
Sundar Iyer, Nick McKeown,
``Making Parallel Packet Switches Practical", 
{\it Proceedings of IEEE INFOCOM}, Alaska, April 2001, vol. 3, pp. 1680-87.


    \item 
Sundar Iyer, Ramana Rao Kompella, Ajit Shelat,
``ClassiPI: An Architecture for Fast and Flexible Packet Classification", 
{\it IEEE NETWORK, Special Issue on Fast IP Packet Forwarding and Classification
for Next Generation Internet Services}, Mar-Apr. 2001. 

    \item 
Sundar Iyer, Ajay Desai, Ajay Tambe, Ajit Shelat, 
``ClassiPI: A Classifier for Next Generation Policy Based Engines", 
{\it IEEE Hot Chips}, Stanford University, Aug 2000.

    \item Sundar Iyer, Amr. A. Awadallah, Nick McKeown,
``Analysis of a Packet Switch with Memories Running Slower than the Line Rate", 
{\it Proceedings of IEEE INFOCOM}, Tel Aviv, March 2000, pp.529-537.

    \item 
``Practical Algorithms for Performance Guarantees in Buffered Crossbars", with
Shang-Tse Chuang, Nick McKeown, {\it IEEE INFOCOM 2005}.
\end{enumerate}

\subsubsection*{INVITED PAPERS}
\begin{enumerate}

    \item 
Sundar Iyer, Nick McKeown,
``Maximum Size Matchings and Input Queued Switches", 
{\it Proceedings of the 40th Annual Allerton Conference on Communication, Control, and Computing}, Monticello,
Illinois, Oct 2002.

    \item 
D. Shah, Sundar Iyer, Balaji Prabhakar, Nick McKeown,
``Maintaining Statistics Counters in Router Line Cards", {\it IEEE Micro,} Jan-Feb, 2002, pp. 76-81. Also appeared as ``Analysis of a Statistics
Counter Architecture"  in {\it IEEE Hot Interconnects}, Stanford University, Aug. 2001.

\end{enumerate}


\subsubsection*{PAPERS UNDER REVIEW}
\begin{enumerate}

    \item 
Sundar Iyer, R. R. Kompella, Nick McKeown,
``Designing Packet Buffers for Router Line Cards", 
{\it IEEE/ACM Transactions on Networking}. Presently available as, 
{\it HPNG Technical Report - TR02-HPNG-031001}, Stanford University, Mar.
2002.
\end{enumerate}


\subsubsection*{PENDING PAPERS}
\begin{enumerate}

    \item 
``Attaining Statistical and Deterministic Switching Guarantees using Buffered
Crossbars", with Shang-Tse Chuang, Nick McKeown. In preparation for {\it IEEE/ACM Transactions on Networking}.

    \item 
``Maintaining State in Router Line Cards", with Nick McKeown. In preparation for
{\it IEEE Communication Letters}.
\end{enumerate}

\subsubsection*{OTHER REPORTS}

\begin{enumerate}
\item
Sundar Iyer, Nick McKeown
``Techniques for Fast Shared Memory Switches", 
{\it HPNG Technical Report - TR01-HPNG-081501}, Stanford University, Aug 2001. 

\item
Sundar Iyer,
``The Parallel Packet Switch Architecture", 
{\it Masters Thesis Report}, May 2000, Stanford University.
\end{enumerate}

% This resets the counter for the enumerate environment.
\myEnumReset 

%\vspace{0.1cm}
\subsection*{PATENTS \& APPLICATIONS}
\hrule
\vspace{0.2cm}

  These patents were applied for when working in Industry. All patent applications are 
in processing, except when mentioned otherwise.
%\footnote {None of the research done at Stanford has been patented, they are all freely
%available for use in the public domain.} 
%Among others, our content processing algorithms are in use in Cisco's Content Services Switches.

\begin{enumerate}

    \item {\bf Network Memory}

	\begin{itemize}
    	\item Multiple patents filed for various algorithms and techniques for
the design of network memory. Details of these patents are available on request.
	\end{itemize}

    \item {\bf Network Address Translation}

	\begin{itemize}

    	\item  {\it (granted)} Subhash Bal, Raghunath Iyer, Sundar Iyer, ``Method and
Apparatus for Performing Internet Network Address Translation", U.S.
Patent-6457061. Filed Nov. 1998, Issued Sep. 2002.

	\end{itemize}

    \item {\bf Pattern Matching}

	\begin{itemize}

    	\item Sundar Iyer, Ajit Shelat, George Varghese et al.,
``Fast, Deterministic Exact Match Look-ups In Large Tables". Filed Oct. 2002.

	 \item Sundar Iyer, Ajit Shelat, George Varghese  et al., ``Method and Apparatus
for Parallel String Searching". Filed May. 2000.

	\end{itemize}

    \item {\bf Route Lookup and Packet Classification}

	\begin{itemize}

    		\item Sundar Iyer, Ajit Shelat et al.,
``Algorithm and Design for Deterministic Parallel Route Lookups". Filed Jul. 2001.

    		\item Sundar Iyer, Moti Jiandani, Ajit Shelat et al., 
``Control System for High Speed Rule Processors". Filed Apr. 1999.

    		\item {\it (granted)} Sundar Iyer, Ajit Shelat et al.,``Method and Apparatus
for High-Speed Network Rule Processing using an Array of Cells - II". U.S. Patent-6510509.
Filed Mar. 1999, Issued Jan. 2003.

    		\item Sundar Iyer, Moti Jiandani, Ajit Shelat et al., ``Method and Apparatus
for High-Speed Network Rule Processing- I". Filed Dec. 1998.

	\end{itemize}

    \item {\bf Deflection Routing}

	\begin{itemize}

        \item Sundar Iyer, Supratik Bhattacharrya, Nina Taft, Christophe Diot,
``A Method to Alleviate Link Overload on an IP Backbone". Filed July 2003.
	\end{itemize}


\end{enumerate}

\myEnumReset 


%\vspace{0.1cm}
\subsection*{TALKS}
\hrule
\vspace{0.2cm}

\subsubsection*{CONFERENCE TALKS}
\begin{enumerate}
    \item
       {\it (Pending)} ``An Approach to Alleviate Link Overload as Observed on an IP Backbone",
       {\it IEEE INFOCOM 2003}, San Francisco, California, Apr. 2003. 

    \item 
       {\it (Invited)} ``Maximum Size Matchings and Input Queued Switches",
       {\it 40th Annual Allerton Conference on Communication, Control, and Computing}, Monticello, Illinois, October 2002. 

    \item
       ``Routers with a Single Stage of Buffering",
       {\it ACM SIGCOMM}, Pittsburgh, Pennsylvania, Aug 2002. 

    \item 
       ``Analysis of a Statistics Counter Architecture",
       {\it IEEE Hot Interconnects}, Stanford, California, Aug. 2001. 
    \item 
       ``Analysis of a Memory Architecture for Fast Packet Buffers",
       {\it IEEE - High Performance Switching and Routing}, Dallas, Texas, May 2001. 
    \item 
       ``Making Parallel Packet Switches Practical",
       {\it IEEE INFOCOM 2001}, Anchorage, Alaska, USA, April 2001.
    \item 
       ``Techniques for Fast Packet Buffers",
       {\it IEEE - GBN Workshop 2001}, Anchorage, Alaska, USA, April 2001.
    \item 
       ``ClassiPI: A Classifier for Next Generation Content/Policy Based Switches",
       {\it IEEE Hotchips}, Stanford, California, August 2000.
    \item 
       ``Co-processors and the role of specialized hardware",
       {\it NETWORLD + INTEROP 2000}, Las Vegas, Nevada, May 2000.
    \item 
       ``Analysis of a Packet Switch with memories running slower than the line-rate",
       {\it IEEE INFOCOM 2000}, Tel Aviv, Israel, March 2000. 
\end{enumerate}

\subsubsection*{INDUSTRY/OTHER TALKS}
\begin{enumerate}
   \item 
       {\it (various venues)} ``Analysis of the Parallel Packet Switch Architecture", 
	\begin{itemize}
   	\item {\it (Invited)} Dept. of Electrical Engineering, I. I. T. Bombay, India - Dec. 2001.
        \item SwitchOn Networks, Pune, India - Sep. 1999.
        \end{itemize}

   \item 
       ``Requirements for a packet classification API", 
       Network Processor Forum (CPIX), Denver, Colorado - Mar. 2001.

   \item 
       {\it (various venues)} ``Designing Packet Buffers for Networking",
	\begin{itemize}
        \item Rambus Inc., Los Altos, California - Apr. 2001, Sep. 2002.
        \item Infineon Technologies, San Jose, California  - Apr.  2002, May
2002.
        \item Juniper Networks, Sunnyvale, California - Apr. 2001.
        \item University of California Davis, Davis, California  - Oct 2002.
        \end{itemize}
 
   \item 
        ``Some Observations towards Load Balancing over a Network",
       Sprint ATL Retreat, San Francisco, California, Aug. 2001.
   \item 
       ``Shortest Path Routing via Alternate Nearest Neighbor", Sprint ATL 
       Retreat, Lake Tahoe, California, Mar. 2002.

   \item 
     ``Analyzing CIOQ Switches using the Constraint Set Technique", Stanford
University, California, Feb. 2002. 

   \item 
     ``Practical Algorithms for Performance Guarantees in Buffered Crossbars", Stanford
Networking Seminar, California, Jan. 2003. 

\end{enumerate}

%\vspace{0.1cm}
\subsection*{PROFESSIONAL ACTIVITIES}
\hrule
\vspace{0.2cm}
\begin{itemize}
	\item Technical Program Committee Member, QoS-IP, Milano, Italy, 2003.
	\item Member Network Processing Forum (Originally CPIX) - 2000-2001.
\end{itemize}

%\vspace{0.1cm}
\subsection*{SERVICE}
\hrule
\vspace{0.2cm}
\begin{itemize}
	\item Reviewer (Journals) - {\it IEEE/ACM Transactions on Networking,
IEEE Journal on Selected Areas in Communications, IEEE Network, Computer
Networks, IEEE Communication Letters, Journal of High Speed Networks.}
	\item Reviewer (Conferences) - {\it IEEE INFOCOM 2000, 2001, 2002, 2003,
IEEE Hot Interconnects 2001, IEEE Globecom 2000, ACM SIGMETRICS 2003, ISCA 2003,
HPSR 2003}
\end{itemize}

% \begin{multicols}{3}[\section*{Long title across all the columns}]

%\vspace{0.1cm}
\subsection*{LANGUAGES}
\hrule
\vspace{0.2cm}
\begin{list}{}{}
	\item  Proficient in English, Hindi and Marathi. Working knowledge of Tamil and German.
\end{list}

%\newpage

\vspace{0.1cm}
%\begin{multicols}{2} [\subsection*{REFERENCES}]

\subsection*{REFERENCES}
\hrule
\vspace{0.2cm}


\subsubsection*{FROM ACADEMIA}
\begin{footnotesize}

\begin{multicols}{2} 
\noindent 
Prof. Nick McKeown \\
Associate Professor \\
Dept. of Electrical Engg. \& Comp. Sc. \\
353 Serra Mall, Room 340 \\
Stanford, CA 94305 \\
Phone: (650) 725-3641 \\
nickm@stanford.edu \\

\noindent
Prof. Balaji Prabhakar\\
Assistant Professor \\
Dept. of Electrical Engg. \& Comp. Sc. \\
350 Serra Mall, Room 269 \\
Stanford, CA 94305-9510 \\
Phone: (650) 723-6579 \\
balaji@stanford.edu \\

\columnbreak

\noindent
Prof. George Varghese\\
Professor \\
Dept. of Comp. Sc. \& Engg., MS 0114 \\
9500 Gilman Drive, UC San Diego \\
La Jolla, CA 92040-0114 \\
Phone: (858) 822-0424 \\
varghese@cs.ucsd.edu \\


\noindent
Prof. Rajeev Motwani \\
Professor \\
Dept. of Computer Science  \\
353 Serra Mall, Room 474 \\
Stanford, CA 94305 \\
Phone: (650) 723-6045 \\
rajeev@cs.stanford.edu \\

\end{multicols}

%\begin{tabbing}
%xxxx\=xxxxxxxxxxxxxxxxxxxxx\=xxxx\=xxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxxx\=\kill
%\>{Nick McKeown}\> :\>nickm@stanford.edu\\
%\>{Balaji Prabhakar}\>:\>balaji@stanford.edu\\
%\>{Ajit Shelat}\>:\>ajit\_shelat@pmc-sierra.com\\
%\>{S.S.S.P. Rao}\>:\>ssspr@cse.iitb.ernet.in\\
%\end{tabbing}
%\newpage

\end{footnotesize}
\end{small}
\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
