\documentclass[letterpaper, 10pt]{article}
\topmargin-2.0cm

\usepackage{fancyhdr}
\usepackage{lastpage}
\usepackage{xspace}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}

% Color Information from -
% http://www-h.eng.cam.ac.uk/help/tpl/textprocessing/latex_advanced/node13.html

\advance\oddsidemargin-1in
%\advance\evensidemargin-0.65in
\textheight9.2in
\textwidth6.9in
\newcommand\bb[1]{\mbox{\em #1}}
\def\baselinestretch{1.05}

\newcommand{\hsp}{\hspace*{\parindent}}
\definecolor{gray}{rgb}{0.4,0.4,0.4}

\begin{document}
\thispagestyle{fancy}

% Leave Left and Right Header empty.
\lhead{}
\rhead{}

\renewcommand{\headrulewidth}{0pt} \renewcommand{\footrulewidth}{0pt}
\fancyfoot[C]{\footnotesize
\textcolor{gray}{http://www.cs.columbia.edu/$\sim$jikk/application}}

\pagestyle{fancy}
\lhead{\textcolor{gray}{\it Kangkook Jee}}
\rhead{\textcolor{gray}{\thepage /\pageref{LastPage}}}

%Macros of my own
\def\libdft{libdft\xspace}
\def\TFAFull{Taint Flow Algebra\xspace}
\def\TFA{TFA\xspace}
\def\SR{ShadowReplica\xspace}
\def\ie{i.e.,\xspace}

\newif \ifcomments
%\commentstrue

\ifcomments
\newcommand{\jikk}[1]{{---\textcolor{red}{#1}---}}
\else
\newcommand{\jikk}[1]{}
\fi
%

% This kind of makes 10pt to 9 pt.
\begin{small}

%\vspace*{0.1cm}
\begin{center}
{\LARGE \bf RESEARCH STATEMENT}\\
\vspace*{0.1cm}
{\normalsize Kangkook Jee (jikk@cs.columbia.edu)}
\end{center}
%\vspace*{0.2cm}

%\begin{document}
%\centerline {\Large \bf Research Statement for Kangkook Jee}
%\vspace{0.5cm}

% Write about research interests...
%\footnotemark
%\footnotetext{Check This}

The task of building secure and reliable computing environment is getting
harder and harder most notably for failing to propose a security system that
addresses the following properties simultaneously.

\begin{itemize}

        \item {\bf Effectiveness} in detecting and preventing software failures
                caused either by active exploitation of malicious attackers or
                unintended disclosure of developer bugs.

        \item {\bf Efficiency} by having minimal amount of resource
                overhead~(e.g., power, response time) to make the security
                solution adoptable to the production environment.

        \item {\bf Coverage} in providing end-to-end protection. For instance,
                security system should protect the entire software execution
                stack supporting COTS binaries with no source access.

\end{itemize}

The rapid evolution of computer systems only exacerbates the problem as it
constantly re-defines our notion about the computing environment.
%
Many industry vendors as well as research communities have driven the
innovations in this line of research and this is the
space in which my research interest is.

My main research contributions have been concretized over the past a few years
as I developed and improved well-known security architecture of data flow
tracking~(DFT) that supports COTS binaries with no source access.
%
To address the issue of high overhead inherent to the systems of the same kind,
I leveraged a number of recent research innovations from different software
system layers. Specifically, I have been interested in combining static and
dynamic analysis approaches.
%
Although my research have focused on a specific security system of DFT, I
believe that the insights that I learned from it can benefit the area of system
security in general since DFT shares many architectural characteristics with
other security systems.

In addition to making improvements for a dynamic security system, I have a
broader interest in research topics related to secure and reliable software
environment.
%
First of all, it is crucial to improve static analysis techniques such as
whitebox and blackbox software fuzzing to assist developers as well as security
professionals. 
%
We also need to improve educational system to have our students better
understandings about various security and reliability issues. 
%
In my view, the goal of building secure computing environment can be attained
not by any single research direction but by holistic consideration of a number
of different approaches including aforementioned ones.

My long-term research will be about design and implementation of the security
architecture which would impact everyone's computing life by providing trusted
computing service at the expense of the negligible runtime slowdown.  
%
The approach that I am currently focusing on is to take advantage of the static
analysis techniques to improve the dynamic defense measures. 
%
The other way around, executions from dynamic component would guide the static
counterpart to achieve better coverage and accuracy.
%
%Complementing one another, I am confident that we are getting closer to the
%goal of building secure and reliable system effective in countering wide range
%of attack vectors~(often unpredictable) only requiring minimal amount of
%overhead. 
%
Providing such service with complete coverage~(e.g., support for COTS binaries
and for full execution stack) is another design goal.
%
From my research results thus far, I believe that I have already opened up the
promising perspectives in this research direction.

In the next a few paragraphs, I describe my past works, current interests, and
future research directions in the area of system security.

\subsection*{Data Flow Tracking(DFT) System Innovations}
% Paragraph 1: A brief paragraph sketching the overarching thematics and topic
% of your research, situating it disciplinary.
%
DFT has been my main research topic which I extensively explored various
aspects of the technology for its {\bf effectiveness} in serving many different
problem domains as well as for its {\bf efficiency} in making it more adoptable
to consumer and production systems.
%
%Typical DFT system is composed of three different operations; {\it i)} {\it
%tagging} input variables come in though any untrusted sources, {\it ii)} {\it
%propagating} tag values associated to the variables as the program executed,
%{\it iii)} {\it checking} for unintended usages of tagged variables. 
%
Our DFT implementations inject their operations using VM-based instrumentation
framework, which is PIN Dynamic Binary Instrumentation~(DBI)~\cite{pin}, to
apply the technology to COTS binaries with no source access~({\bf
coverage}).
%
Besides implementing DFT system that correctly operates, I invented number of
novel optimizations and architectures that alleviate its excessive slowdown
which is inherent to DFT and system security tools of the same kind. And this
is what I consider as the main contribution of my research.

% libdft
%\subsubsection*{\libdft: High performance fine-grained DFT system for COTS
%software}

\libdft~\cite{libdft:2012vee} is our initial prototype implementation for DFT
that propagates tag values in byte granularity.
%
With its generic API, \libdft enables users to build tools that fulfill their
own demand. 
%
%It implements a process-level protection~(in contrast to system-wide) by
%injecting DFT logic for each {\it x86} instruction leveraging VM-based
%instrumentation framework.
%
Core to \libdft's performance improvement is in understanding the precise
definition of taint propagation semantics for {\it x86} instruction set as well
as the structural limitations of VM-based instrumentation layer. 
%
%\libdft addresses these issues by introducing optimal tracking codes
%customized for different types of {\it x86} instructions. 
%
Two main considerations that we made for the implementation are {\it i)}
minimization of the cost required for context switching between the original
application and DFT analysis contexts and {\it ii)} efficient design and
management of shadow memory space.
%
Evaluation for the prototype shows $\sim$10$\times$ - $\sim$11$\times$ slowdown
over the native execution for a number of standard benchmark suites and this
was a significant performance improvement over previous DFT implementations by
the time we introduced the system.\jikk{more justification needed for this
statement}

% TFA (Taint Flow Algebra)
%\subsubsection*{\TFA: A framework for principled optimizations for DFT}

Even with the highly crafted tracking logics that we invented for \libdft, its
operation still remained sub-optimal for not being able to address the
fundamental limitations common to up-to-date DFT implementations. 
%
These are about lacking in understandings for {\it i)} the global context of
DFT operations and {\it ii)} the semantics of DFT operations which is clearly
different from that of the original program execution.
%
\TFAFull~(\TFA)~\cite{tfa:2012ndss} is a special purpose Intermediate
Representation~(IR) that captures DFT logics extracted from the original {\it
x86} binary. With this representation, we apply a number of traditional
compiler optimizations as well as DFT specific optimizations that we developed
to address aforementioned limitations.
%
To apply optimizations, we designed a framework composed of two distinct
sub-components.  The first one is the static analysis component run from
off-line analysis phase to prepare the optimized DFT logics. The second one is
the dynamic runtime component to enforce the optimized DFT operations back to
the original program at runtime.
%
% may want to mention about 'feedback loop' connecting two components.
%
As a result, TFA could achieve \(\sim\)~2\(\times\) performance improvement
over  our baseline tool~(\libdft) when it is evaluated against the same set of
standard benchmark suites without compromising the correctness\footnote{In
        this context, by {\it correctness}, we ensure the same level of the
security guarantee that the baseline tool~(\libdft) would provide.} of DFT
operations.

% ShadowReplica
%\subsubsection*{\SR: A framework for parallelized execution of DFT}
%
Given that \TFA represents DFT logics extracted from the original program to
apply a number of optimization approaches, \SR~\cite{sreplica:2013ccs} extends
\TFA approach further to have more performance gain by running the original
program and the extracted DFT logics from two separate CPU cores.
%
%Of course, we are not the first one who are aligned toward the approach of
%parallelized DFT analysis, but the most of previous proposals failed to
%achieve expected performance improvement mainly due to the high communication
%overhead connecting two different execution contexts. In most cases, the cost
%overwhelms the parallelization benefit by causing to require excessive amount
%of resources to make the system suitable for online deployment.
%
The main contribution of \SR project lies in addressing the issue of high
communication overhead and proposing a framework  to defend against any
software failures/exploitations at runtime. Different from previous proposals,
the system only requires a single analysis thread per an application thread and
the analysis thread that executes TFA representation runs at the same or faster
speed than the application thread making synchronization between two different
threads easier.
%
In \SR project, we again dedicate static analysis phase {\it i)} to have DFT
logic extracted from the target application and represent them in \TFA\xspace
{\it ii)}  to minimize the volume and frequency of the communication
requirement connecting two threads.
%
Architectural consideration also matters in designing the communication
channel, otherwise the channel would become a performance bottleneck as it
fails to schedule two threads competing for the shared resource of CPU caches.
%
As a result, \SR framework could improve the overhead by $\sim$2$\times$,
$\sim$4$\times$ over \TFA and \libdft respectively when it is evaluated for the
same standard benchmark suites, achieving $\sim$2.75$\times$ slowdown over the
native execution.

Interestingly, although \SR uses additional CPUs for better performance, the
entire framework consumes the same or less amount of CPU cycles~(or powers)
than that of comparable in-lined DFT implementation~(\TFA) for the same
analysis.
%
In this case, the benefit of having smaller instrumented code for event
collection~(when it is compared to the size of code of in-lined DFT analysis)
and its subsequent performance saving surpassed the extra CPU cycles it pays to
establish the communication channel and exchange data between two threads.

\subsection*{Current research} %: Practical and accurate security architecture}
%
%My main research interest lies in the area of the system security in general
%that serves for the safety and reliability of software systems and I could
%have accumulated in depth insights and experiences about number of
%technologies throughout my research career.
%

I briefly describe my ongoing research to improve dynamic security systems~(\ie
DFT and of the same kind). The efforts are made in twofolds.  The one is to enhance
instrumentation layer mainly to address the overhead issue. The other is to
implement a measurement framework that evaluates the accuracy of dynamic
security systems. 

%would help readers to have better understanding about my research direction.

\subsubsection*{A comparison study of DBI frameworks for security applications}
%
Oftentimes, security researchers choose one of the following three Dynamic
Binary Instrumentation~(DBI) frameworks -- PIN~\cite{pin},
DynamoRIO~\cite{dynamorio}, and Valgrind~\cite{valgrind} -- as their
instrumentation medium when they need to in-line their security/monitoring
logic to COTS binaries.
%
In this project, we carry out a comparison study that investigates various
aspects of these DBI frameworks. As their behavioral and performance
implications significantly differ by each one's design philosophy and intended
problem domain, we propose number of criteria~(e.g., userability,
effectiveness, capability, and efficiency) to empirically evaluate.

%
The goal of the project is to provide a guideline for users who want to find a
instrumentation framework that serves for their demand.

\subsubsection*{General architecture of parallelized analysis} 
%
DFT is an instance of security system that resorts to VM-based instrumentation
and suffers from high overhead.
%
Currently, we are working on a project that extends \SR approach by defining
common API to support other analyses expecting to have similar performance gain
as DFT did. 
%
As a first step, it will support Control Flow Integrity~(CFI) and
memory integrity tool~\cite{memcheck}, then we will look for more security
analyses.

\subsubsection*{Further performance acceleration approaches}
%
Even though our research could make substantial amount of performance
improvement for DFT system, I should admit that we have not yet reached the
point where industry and research community would regard it as adoptable to
their production systems.
% - the following may be redundant.
%And there is a consensus around research communities that whatever benefit the
%security system would bring to its users, $5\%$ overhead is a threshold that
%would prevent the system being adapted as a production
%system.~\cite{ccs2013:invited_talk}
%
For DFT implementation and else security architectures of the same kind, I
could indicate two major overhead sources; {\it i)} the cost for VM-based
instrumentation and {\it ii)} the cost for shadow memory management~(mainly
occurs as it translates real address to it counterpart shadow address).
%
Currently, I am working on projects of two different kinds to address these
issues. The first one resorts to additional hardware component and the second
one proposes a new hybrid instrumentation framework, a software only solution
that combines source-based and binary-only instrumentation.

{\bf Hardware-assisted \SR:} 
%
%Although \SR minimizes the size of the code instrumented, the cost for
%original application execution along with instrumented code for event
%collection still takes up the large portion of the system's overall slowdown.
%Second to this, the cost for shadow memory translation also incur
%non-negligible amount of computations.
%
This is a H/W system that introduces another pipeline stage to record required
information and transfer it to a different core. This would eventually replace
the in-lined event collector and connecting communication channel of \SR.
Another H/W component that we need is a new instruction that would assist
real-to-shadow address translation. The important design criteria for this
project is to maintain the additional hardware component minimal and flexible
so as it can be extended to support different types of analysis with simple
modification from software layer.
 
{\bf Hybrid instrumentation framework:} This is a software only approach that
proposes a new instrumentation framework that maximize the benefit of
available~(partial) source access still supporting COTS binaries.
%
This combines two different instrumentation approaches into a single framework.
We use LLVM compiler pass and DynamoRIO DBI to support source-based and
binary-only instrumentation respectively.
%
This hybrid approach introduces number of interesting research challenges that
include how to maintain a single execution context integrating two very
different instrumentation approaches and support uniform API interface to
users. 

%
%Intuition behind this idea is that in most cases, we have partial accesses to
%source base feasible for compiler-based instrumentation known to be several
%times faster than VM-based instrumentation, and for the rest of execution
%environments(which we do not have source access), we can use VM-based
%instrumentation to maintain completeness.

\subsubsection*{Evaluation framework the soundness of DFT analyses}
%
Although DFT has gained many attentions from research communities for its known
effectiveness, its {\it soundness} issue in terms of correct information flow
has not been explored thoroughly and the question about the existence and
frequency of incorrect flows~(false positives or false negatives) remains
unanswered. From this work, we introduce a new methodology to evaluate the
soundness of DFT systems and build an evaluation framework prototype. 
%
The framework composed of two sub-components of {\it i)} taintedness
measurement component that evaluates different information flows and {\it ii)}
the input generation system that guides the measurement component leveraging
the symbolic execution approach.\jikk{some more texts needed.}
%
In this project, we are planning to apply the methodology to evaluate a number
of different DFT systems implemented for Android operating system.

\subsection*{Summary} 
%
In the course of my research, I could establish in depth experience and insight
about DFT system, a popular system security topic that shares its core
characteristics with many other security architectures.
%
In effort to make the technology closer to the production deployment, I also
invented number of novel optimization techniques and frameworks that combine
static and dynamic analysis approaches.
%
Besides DFT, I am also interested in topics that would harden software systems
and make them immune to exploitable defects or unintended bugs. 

For my future research, I am eager to broaden my research experience
exploring various static and dynamic analysis techniques combining these to
serve for the single goal of secure and reliable system design.

\end{small} 

%\newpage

%refer to http://sites.stat.psu.edu/~surajit/present/bib.htm
\bibliographystyle{plain}
\bibliography{res}
\end{document}
