% !TEX root = proposal.tex
\section{Hypothesis} \label{sec:hypo} 

In this section, I discuss about hypotheses that we want to verify and confirm
from my thesis.

\subsection{\sreplica Generalization}

Even though, our previous work most focuses on a specific instance of inline
monitor (\ie DFT), we strongly believe that the approaches can easily be
generalized to support analyses of other kinds only with minimal amount of
effort.  Tabel~\ref{tab:analyses} contains a list of well-known inline
monitors~\cite{CAB} echo one's goal is either to protect or profile application
processes dynamically. Column entries categorizes monitors according to its
structural properties. Column entry {\it Shadow Memory} denotes whether the
monitor requires shadow memory area to keep track of updates from real
execution context. {\it Data dependency} denotes whether the monitor's
operations depend on it own previous updates. We have to consider data
dependencies between updates if we want to parallel the analysis performed by
the monitor. {\it Check Operation} denotes whether the monitor examines for
specific system activities. For instance, DTA tool checks for every {\tt RET}
structions to see whether a taintedness value is used for its operand to
deviate executions. In contrast, {\it cache simulation} does not have such
operations.

\begin{table}[h]
\begin{tabular}{|c|c|c|c|}
\hline
Analyses & Shadow Memory & Data Dependency & Check Operation \\ 
\hline \hline
Data Flow Tracking (DFT) & O & O & O \\ \hline
Control Flow Integrity (CFI) & O & O & O \\ \hline
\specialcell{Memory Integrity Tool \\ (Memcheck)} & O & O & O \\ \hline
LockCheck & O & O & O \\ \hline
Method Counting & O & O & O \\ \hline
Call Graph Profiling & O & O & O \\ \hline
Path Profiling & O & O & O \\ \hline
Cache Simulation & O & O & O \\ \hline
\end{tabular}
\caption{ categorizes different inline analyses based on requiring {\it shadow
memory}, analysis' {\it dependency to its previous operations}, existence of
{\it checking/asserting operations}. \label{tab:analyses}}
\end{table}

Our goal here is to extend \sreplica approach to support most of monitors
presented from Table~\ref{tab:analyses}. Eventual output would be a generalized
framework with supporting API that helps users to write tools that serve for
their needs. However, due to time and resource constraints, we are planning to
build proof-of-concept implementation by extending \sreplica to support
representative instances of control flow integrity (CFI)~\cite{} and memory
integrity tool~\cite{}.

\subsubsection{Control Flow Integrity (CFI)} 

CFI thwarts control-hijacking attacks by ensuring that the control flow remains
within the control-flow graph (CFG) intended by the programmer. Every
instruction that is the target of a legitimate control-flow transfer is
assigned a unique identifier (ID), and checks are inserted before control-flow
instructions to ensure that only valid targets are allowed. All programs
usually contain two types of control-flow transfers: direct and indirect.
Direct transfers have a fixed target and they do not require any enforcement
checks. However, indirect transfers, like function calls and returns, and
indirect jumps, take a dynamic target address as argument. As the target
address could be controlled by an attacker due to a vulnerability, CFI checks
to ensure that its ID matches the list of known and allowable target IDs of the
instruction. 

A certain form of control flow tracking is already implemented from the current
prototype of \sreplica since it is designed to replicate the execution trace of the original application thread at BBL level granularity.

\subsubsection{Memory Integrity Tool (Memcheck)}

\begin{table}[h]
        \centering
\begin{tabular}{|l|l|}
\hline
{\bf Instruction} & {\bf Tag propagation rule} \\ \hline \hline
    {\tt \specialcell{ALU-OP OP1 $\leftarrow$ OP2 \\ (add, sub \dots)}} & 
    {\tt t(op1) $\vert=$ t(op2)}\\ \hline
    {\tt MOV OP1  $\leftarrow$  OP2} & {\tt t(op1) = t(op2)}     \\ \hline
    {\tt LOAD OP1 $\leftarrow$ [OP2]} & {\tt t(OP1) = t([OP2])}  \\ \hline
    {\tt STORE [OP1] $\leftarrow$ OP2} & {\tt t([OP1]) = t(OP2)} \\ \hline
\end{tabular}
\caption{presents an interpretation of DFT semantics for pseudo instruction set
architecture.}
\label{tab:dft_tracking}
\end{table}

\subsection{Instrumentation Infrastructure Study}
\subsubsection{DBI Study}
\subsubsection{DTrace Instrumentation}
\subsubsection{Hardware Assisted Parallel Analysis}
\subsection{Overhead Modeling Framework}
